PK object batch mode trial

### 2023-08-24 data-raw/batchMode_trial_gpm.Rmd
Added explicit dplyr::n() call to fit_group so it works with multidplyr parallelization and adding explicit definitions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
set.seed(2023)
library(tidyverse, quietly = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
tidyverse_conflicts()
```

@@

# Write into package
evaluate_choices <- function(obj) {
  pk_name <- get_choices(obj)

@@

my_pk_101p <- do_fit(my_pk_101p) %>% evaluate_choices()

@@

# Run all at once
{
current_pk <- my_pk_101p # Define current evaluated pk object here
winning_model_final <- bind_rows(winning_model_final, current_pk[[1]])
rmse_summary <- bind_rows(rmse_summary, current_pk[[2]])
detail_stats <- bind_rows(detail_stats, current_pk[[3]])
rm(current_pk)
gc()
}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
set.seed(2023)
library(tidyverse, quietly = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
library(multidplyr)
tidyverse_conflicts()
```

@@

# Write into package
evaluate_choices <- function(obj, PJ = "Pooled") {
  pk_name <- get_choices(obj, PJ = PJ)

@@

my_pk_101p <- do_fit(my_pk_101p) %>% evaluate_choices() # Done

my_pk_000j <- do_prefit(my_pk_000j)
my_pk_000j <- do_fit(my_pk_000j) %>% evaluate_choices() # Done (took 16 minutes)
# WOW! A 2-3X speedup from the previous sapply() implementation
my_pk_100j <- do_fit(my_pk_100j) %>% evaluate_choices(PJ = "Joint") 
my_pk_110j <- do_fit(my_pk_110j) %>% evaluate_choices()
my_pk_111j <- do_fit(my_pk_111j) %>% evaluate_choices()
my_pk_010j <- do_fit(my_pk_010j) %>% evaluate_choices()
my_pk_011j <- do_fit(my_pk_011j) %>% evaluate_choices()
my_pk_001j <- do_fit(my_pk_001j) %>% evaluate_choices()
my_pk_101j <- do_fit(my_pk_101j) %>% evaluate_choices()

@@

# Run all at once
{
current_pk <- my_pk_000j # Define current evaluated pk object here
winning_model_final <- bind_rows(winning_model_final, current_pk[[1]])
rmse_summary <- bind_rows(rmse_summary, current_pk[[2]])
detail_stats <- bind_rows(detail_stats, current_pk[[3]])
rm(current_pk)
gc()
}
